Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-29 report/report.tex
Update todo
Add footpath vs other highway categories conclusion
Include images showin feature overlap fix algorithms

% REPORT
% TODO: Enter correction data in report
% TODO: Analysis, write about the building-road case
% TODO: Analysis, write about the road-road case
% TODO: Plot features before collision, building-road
% TODO: Plot features before collision, road-road
% TODO: Proposed fixing algorithm: building-road
% TODO: Proposed fixing algorithm: road-road
% TODO: Analysis, mention that footpaths were nor worse than other categories, which are included in many unity packages already
% TODO: Figure, suggested morphing, building-road case
% TODO: Figure, suggested morphing, road-road case
% TODO: Proof read report

@@

All these cases will create issues when generating the 3D mesh representation of the city.

>>>>

% REPORT
% TODO: Proposed fixing algorithm: building-road
% TODO: Proposed fixing algorithm: road-road
% TODO: Mention propagation of error, have to include all the edited features in the next pass
% TODO: Proof read report

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_feature_overlap_fix_1}
    \caption{}
    \label{fig:space}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_feature_overlap_fix_2}
    \caption{}
    \label{fig:space}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_feature_overlap_fix_3}
    \caption{}
    \label{fig:space}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_feature_overlap_fix_4}
    \caption{}
    \label{fig:space}
\end{figure}

All these cases will create issues when generating the 3D mesh representation of the city.
Conslusion: footpaths were not worse than other categories, which are included in many unity packages already
